## Preface {.unnumbered}

The ggplot2 cookbook was formatted using the Quarto Document in Rstudio. To learn more about Quarto books visit <https://quarto.org/docs/books>.

I assume you have already installed R (https://www.r-project.org) (R Core Team 2022) and the RStudio IDE (https://www.rstudio.com).

Next you can install the **rmarkdown** package in R:

```{r}
## Install from CRAN
#install.packages('rmarkdown')

## Or if you want to test the development version,
## install from GitHub
# if (!requireNamespace("remotes"))
#   install.packages('remotes')
# remotes::install_github('rstudio/rmarkdown')
```

If you want to generate PDF output, you will need to install LaTeX. For R Markdown users who have not installed LaTeX before, we recommend that you install [TinyTeX](https://yihui.name/tinytex/ "https://yihui.name/tinytex/") :

```{r}
# install.packages('tinytex')
# tinytex::install_tinytex()  # install TinyTeX
```

## 所需程序包

| 程序包       | 安装方法                                                          |
|:-----------------------------------|:-----------------------------------|
| tidyverse    | install.packages("tidyverse")                                     |
| plyr         | install.packages("plyr")                                          |
| ggthemes     | install.packages("ggthemes")                                      |
| ggthemr      | install.packages("ggthemr")                                       |
| ggsci        | install.packages("ggsci")                                         |
| ggtech       | devtools::install_github("ricardo-bion/ggtech",dependencies=TRUE) |
| ggplotAssist | install.packages("ggplotAssist")                                  |
| ggplotgui    | install.packages("ggplotgui")                                     |
| ggpubr       | install.packages("ggpubr")                                        |
| easyGgplot2  | devtools::install_github("kassambara/easyGgplot2")                |
| gridExtra    | install.packages("gridExtra")                                     |
| ggplot2      | devtools::install_github("hadley/ggplot2")                        |

## 参考资料推荐

[ggplot2:Elegant Graphics for Data Analysis](http://www.springer.com/us/book/9783319242750)

[R Graphics Cookbook](http://www.it-ebooks.info/book/1316/)

[ggplot2作图函数参考网址](http://ggplot2.tidyverse.org/reference)
